Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-06-10 SIR_manuscript.tex
adding some refs for testing tracing modeling

\bmb{Leftover comments:
\begin{itemize}
\item should emphasize (at some appropriate point in text) that $\Delta$ is independent of $\beta$ (and hence of $\Rnum$ if we are thinking primarily of holding $\gamma$ constant and varying $\beta$) for the small-$\rho$ (Taylor-expansion) case, see Eq.~\ref{eq:lin}.
\item it would be good to have a few more testing refs: Bergstrom et al., there might be some other stuff we can recycle from the lab meeting review; Friston's stuff deserves to be mentioned because it does have explicit testing flows too. We should try not to ignore/piss anyone off who has already done stuff
\end{itemize}
\ali{:}
Testing dynamics has been previously modeled in the context of epidemiology.
\cite{bergstrom2020frequency} modeled repeated random testing of isolated populations and provided some analytical results.
\citep{friston2021testing} model the effects of self-isolation on testing and tracking.  
 Comparing to these works, our modeling execise is novel. 
}

>>>>

\bmb{Leftover comments:
\begin{itemize}
\item should emphasize (at some appropriate point in text) that $\Delta$ is independent of $\beta$ (and hence of $\Rnum$ if we are thinking primarily of holding $\gamma$ constant and varying $\beta$) for the small-$\rho$ (Taylor-expansion) case, see Eq.~\ref{eq:lin}.
\item it would be good to have a few more testing refs: Bergstrom et al., there might be some other stuff we can recycle from the lab meeting review; Friston's stuff deserves to be mentioned because it does have explicit testing flows too. We should try not to ignore/piss anyone off who has already done stuff
\end{itemize}
}

\ali{This belongs to introduction?}
There have been several modeling works of testing and tracing dynamics and their interaction with epidemiological dynamics. In the context of repeated screaning and random testing of isolated populations (such as a university setup), 
\cite{bergstrom2020frequency} provided some analytical results, 
\cite{rogers2021high} simulated a SEIR model with high-low testing intensity and sensitivity.
Further, \cite{friston2021testing} model the effects of self-isolation on testing and tracking.  
Our modeling approache is novel compared to these works.
